Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1 and ERC project 280053 (CPROVER).}

### 2017-02-03 hscc2017/paper.tex
cut

For the majority of our benchmarks, the conjecture explained in
Section~\ref{synthesis-elements} holds and the two-stage verification 
engine is able to find a stable solution in less than one minute for half
of the benchmarks. This is possible if the inductive solutions need to be 
refined with few counterexamples and increases of the fixed-point precision.  
However, the benchmark \emph{SatelliteB2} with uncertainty ($G_{3b}$)
required too many counterexamples to refine its solution.  
For this particular case, the one-stage engine is able to complement the
two-stage approach and synthesize a solution instead.  It is important to
reiterate that the one-stage verification engine does not take advantage of
the inductive conjecture inherent to CEGIS, but instead fully explores the
counterexample space in one SAT instance.  As expected, this approach is
significantly slower on average and is only useful for benchmarks where
the CEGIS approach requires too many counterexample refinement iterations
such that exploring all counterexamples in a single SAT instance performs better.
Our results suggest an average performance difference of at least two orders
of magnitude between the two engines, leading to the one-stage engine timing
out on the majority of our benchmarks.  Table~\ref{tab:results}
lists the results for both engines independently, where in $16$ out of $23$
benchmarks the two-stage engine is faster.

@@

There is no technique in the existing literature for automatic synthesis of
fixed-point digital controllers that considers FWL effects.  Parameter
synthesis tools such as~\cite{cimatti2013parameter} use bounded model
checking and fixed-point computations to compute parameters based on
user-defined specifications, but they often operate in the continuous domain
and have no direct means of evaluating robustness.

>>>>

For the majority of our benchmarks, the conjecture explained in
Section~\ref{synthesis-elements} holds and the two-stage verification 
engine is able to find a stable solution in less than one minute for half
of the benchmarks. This is possible if the inductive solutions need to be 
refined with few counterexamples and increases of the fixed-point precision.  
However, the benchmark \emph{SatelliteB2} with uncertainty ($G_{3b}$)
required too many counterexamples to refine its solution.  
For this particular case, the one-stage engine is able to complement the
two-stage approach and synthesize a solution instead.  It is important to
reiterate that the one-stage verification engine does not take advantage of
the inductive conjecture inherent to CEGIS, but instead fully explores the
counterexample space in one SAT instance.  As expected, this approach is
significantly slower on average and is only useful for benchmarks where
the CEGIS approach requires too many counterexample refinement iterations
such that exploring all counterexamples in a single SAT instance performs better.
Our results suggest an average performance difference of at least two orders
of magnitude between the two engines, leading to the one-stage engine timing
out on the majority of our benchmarks.  Table~\ref{tab:results}
lists the results for both engines, where in $16$ out of $23$
benchmarks the two-stage engine is faster.

@@

There is no technique in the existing literature for automatic synthesis of
fixed-point digital controllers that considers FWL effects.
%  Parameter
%synthesis tools such as~\cite{cimatti2013parameter} use bounded model
%checking and fixed-point computations to compute parameters based on
%user-defined specifications, but they often operate in the continuous domain
%and have no direct means of evaluating robustness.
